Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
cite => citep

Around 2006, many work on integrating dynamic typing and static typing emerge, 
notably gradual types \cite{siek2006gradual} and hybrid types 
\cite{flanagan2006hybrid}. 
Later \citet{wadler2009well} introduces Blame Calculus, an intermediate 
language for gradual types and hybrid types. 
Blame Calculus throws a blame label when a runtime type-check fails.
Labels provide useful debugging information, therefore are necessary for 
practical use of gradually typed languages.

@@

In 2007, \citet{herman2010space} proposes a solution to this problem by 
representing casts with coercion \cite{henglein1994dynamic}, 
which can be composed and normalized. Every coercion looks like a list of 
trees. For normal coercion, the length of the list is bounded by a small 
constant. And the depths of trees do not grow during composition and
normalization. These two facts implies that coercion is a space-efficient cast 
representation. This coercion, however, does not support blame 
tracking.

@@

So far, it seems that normal coercion is the best way to combine 
space-efficiency and blame-tracking: normal coercion is claimed easy to 
understand \cite{garcia2013calculating}\cite{siek2015blame} and is shown 
easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
Normal coercion is still not satisfactory, however, in at least two aspects.
Firstly, as we mentioned above, it is hard to reason about normal coercion. The 
major difficulty is from its non-structurally recursive composition.
For instance, the developers of Grift report it is tricky to convince
their proof assistants that the composition terminates.

@@

Perhaps unsurprisingly, threesome has a structurally recursive compose and a 
self-standing definition. Together with \citet{garcia2013calculating}'s 
work, they suggest that there might be a cast representation whose definition 
is self-standing, and whose composition is structurally recursive. 
supercoercion introduced in \citet{garcia2013calculating} could be a promising 
candidate. It is believed even more complicated than threesome 
\cite{siek2015blame}. In fact, it uses 10 constructors to deal with an 
elementary type system with only base types and 
function types. And four constructors are directly related to function types. 
Thus, supercoercion might not scale very well to more sophisticated type 
systems.

>>>>

Around 2006, many work on integrating dynamic typing and static typing emerge, 
notably gradual types \citep{siek2006gradual} and hybrid types 
\citep{flanagan2006hybrid}. 
Later \citet{wadler2009well} introduces Blame Calculus, an intermediate 
language for gradual types and hybrid types. 
Blame Calculus throws a blame label when a runtime type-check fails.
Labels provide useful debugging information, therefore are necessary for 
practical use of gradually typed languages.

@@

In 2007, \citet{herman2010space} proposes a solution to this problem by 
representing casts with coercion \citep{henglein1994dynamic}, 
which can be composed and normalized. Every coercion looks like a list of 
trees. For normal coercion, the length of the list is bounded by a small 
constant. And the depths of trees do not grow during composition and
normalization. These two facts implies that coercion is a space-efficient cast 
representation. This coercion, however, does not support blame 
tracking.

@@

So far, it seems that normal coercion is the best way to combine 
space-efficiency and blame-tracking: normal coercion is claimed easy to 
understand \citep{garcia2013calculating}\citep{siek2015blame} and is shown 
easy enough to implement in a compiler \citep{kuhlenschmidt2018efficient}.
Normal coercion is still not satisfactory, however, in at least two aspects.
Firstly, as we mentioned above, it is hard to reason about normal coercion. The 
major difficulty is from its non-structurally recursive composition.
For instance, the developers of Grift report it is tricky to convince
their proof assistants that the composition terminates.

@@

Perhaps unsurprisingly, threesome has a structurally recursive compose and a 
self-standing definition. Together with \citet{garcia2013calculating}'s 
work, they suggest that there might be a cast representation whose definition 
is self-standing, and whose composition is structurally recursive. 
supercoercion introduced in \citet{garcia2013calculating} could be a promising 
candidate. It is believed even more complicated than threesome 
\citep{siek2015blame}. In fact, it uses 10 constructors to deal with an 
elementary type system with only base types and 
function types. And four constructors are directly related to function types. 
Thus, supercoercion might not scale very well to more sophisticated type 
systems.
